---
title: "Lesson_2"
author: "ferjmele"
date: "15 de marzo de 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## New slide
Some content

***
Slide without title

## Heading size test
###Subheading 1
####Subheading 2

Content

## Formatting options

Plain text

**italicized text**

*bold text*

`for (i %in% 1:10){
print(i)
}`

##code example

```{r codex, comment="", eval=FALSE, echo=TRUE}
for (i in 1:10){
print(i)}
```

##plot example

```{r}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="MPG")
```

